Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-13 Arxiv/main.tex
Update main.tex

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
  &$\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

@@

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
\]
we can get the range where we can do better than $\lapmech$ on outputting the correct answer and

\[
\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
\]
we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and

  \item 
  \item 
  \item 
  \item 
\end{itemize}

>>>>

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
 \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

@@

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
\]
we can get the range where we can do better than $\lapmech$ on outputting the correct answer and
\[
\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
\]
we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and

  \item 
\[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
 = 0.11932560927\ or\ 0.11627207896
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.

  \item 
\[
\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.07237464051\ or\ 0.04277410743
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one.

  \item Following equations can be in the same way.
\end{itemize}
